\documentclass[11pt,a4paper,sans]{moderncv}

%% ModernCV themes
\moderncvstyle{casual}
\moderncvcolor{Green}
\renewcommand{\familydefault}{\sfdefault}
\nopagenumbers{}

%% Character encoding
\usepackage[utf8]{inputenc}

%% Adjust the page margins
\usepackage[scale=0.85]{geometry}

%% Personal data
\firstname{Jamie}
\familyname{Gordon}
\title{Software Developer} 
\address{4469 Drayton Lane}{Oviedo, FL 32765} 
\mobile{+1~(386)~852~0156}
\email{jamiesgordon@gmail.com} 
\social[linkedin]{jamiesgordon}
\social[github]{gellaho}

%%------------------------------------------------------------------------------
%% Content
%%------------------------------------------------------------------------------
\begin{document}
\makecvtitle

\section{Education}
\cventry{2010--2015}{Computer Science, BS}{University of North Florida}{Jacksonville}{ \textit{3.85 GPA} }{Dean's List} % arguments 3 to 6 can be left empty
\cventry{2006--2010}{International Baccalaureate Program}{Spruce Creek High School}{Port Orange}{ \textit{4.65 GPA} }{Summa cum Laude} % arguments 3 to 6 can be left empty
\section{Experience}
	\cventry{2013--May 2018}{Software Engineer}{ROI Revolution, Inc.}{Orlando, FL}{}{Worked on tools to help analysts improve online advertising results for ROI's clients. }
	\cvitem{}{\textbf{Achievements:}}
	\cvitem{ \textbf{PUSH} }{An application for managing client product feeds.}
	\cvlistitem{Designed system for downloading and parsing different types of feeds (csv, XML, etc.) from various sources like URLs, FTP locations, and shopping cart APIs}
	\cvlistitem{Built process for users to transform these raw feeds into feeds structured for Google, Bing, and other advertising platforms.}
	\cvlistitem{Automated loading, transforming, and submission of feeds on a scheduled basis using background workers.}
	\cvitem{ \textbf{YARD} }{A system in Elixir for warehousing of Amazon Sponsored Products sales data.}
	\cvlistitem{Downloads and stores historical cost and sales data for various Amazon advertising platforms.}
	\cvlistitem{Parallelized daily report downloads as quickly as possible through Amazon's APIs.}
	\cvlistitem{Also provided an internal API for querying and aggregating overtime sales data for reporting and analysis.}
	\cvitem{ \textbf{EDGE} }{ A Rails Application that automates campaign buildouts for Google AdWords and Bing Adcenter. }
	\cvlistitem{Added interface for seeing unposted campaign elements and managing conflicts.}
	\cvlistitem{Overhauled interface design when upgrading Bootstrap framework from 2 to 3.}
	\cvlistitem{Refactored monolithic database models.}
\section{Skills}
	\cvitem{Ruby}{Significant experience with Ruby on Rails \& JRuby}
	\cvitem{Elixir}{Experienced with concurrency concepts like GenStage \& Flow as well as GenServers and Applications.}
	\cvitem{Postgresql}{Projects are very read \& write heavy and deal with large data.}
	\cvitem{Languages}{Javascript (Node), HTML \& CSS, Java}
	\cvitem{Tools}{Git \& GitHub, Amazon AWS}
	\cvitem{OS}{Windows, Ubuntu Linux, Mac OSX}
	\cvitem{Software}{Word, Excel, and Power Point}
	\cvitem{}{}
%\cvitem{title}{ \emph{Title} }
%\cvitemwithcomment{Language 1}{Skill level}{Comment}
%\cvdoubleitem{category X}{XXX, YYY, ZZZ}{category Y}{XXX, YYY, ZZZ}
%\cvlistitem{Item 1}
%\cvlistdoubleitem{Item 2}{Item 3}
%% ...

%% A publications list
\nocite{*}
\bibliographystyle{IEEEtran}
\bibliography{papers} % a bibtex file containing the list of publications

\end{document}